A Survey Wearable Device Risk Perceptions

### 2015-01-03 wearables_survey.tex
Edited up to 3.1

@@

\section{Methodology}
Our survey consisted of multiple parts. The first section consisted of questions regarding individual and situational concerns with respect to a fictitious wearable device called the ``Cubetastic3000.'' We used this fictitious device as an example in order to minimize any biases that participants might have to specific devices or companies (e.g., visceral reactions to Google Glass based on stories they may have heard in the popular media). The next set of questions focused on individual and situational smartphone concerns. These questions focused on the same scenarios, but we substituted smartphones for wearable technologies in order to see whether participants familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones). The next section of the survey involved performing overall risk/benefit rankings of various wearable technologies relative to better understood technologies. Finally, we collected demographic information, which included general privacy attitudes and whether participants owned any wearable devices. Details on the question ordering, question formatting, and sample questions are discussed in the remainder of this section.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 comprehension questions (attention checks)
\item 6 questions about various wearables scenarios 
\item 2 questions about smartphone scenarios 
\item 2 risk/benefit questions 
\item 15 demographics questions \\[-.8cm]
\end{itemize}

To mitigate any biases, the order in which question groups appeared to the user, the ordering within each group, and, when applicable, the order of the answers for questions, were randomized for each user. Details with respect to the relevant section of the survey are discussed in the respective subsections below.

\subsection{Question Format} 
We talk about the format and justification of the questions from our survey below.

>>>>

{\color{red} You really need to cite ~\cite{Denning2014} in this section.}

{\color{red} To make it flow, add 1-3 sentences here about the gaps in the related work, which then motivates our study (e.g., while people have looked at X, we are aware of no work that has looked at Y. Thus, we performed a survey to examine Y).}

@@

\section{Methodology}
Our survey consisted of multiple sections. In one section, we presented participants with scenarios surrounding a fictitious wearable device called the ``Cubetastic3000,'' and asked them to rate their level of concern for each scenario. We used this fictitious device as an example in order to minimize any biases that participants might have to specific devices or companies (e.g., visceral reactions to Google Glass based on stories they may have heard in the popular media). In another section of the survey, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones). In another section of the survey, we asked participants to compute overall risk/benefit rankings of various wearable technologies relative to better understood technologies. Finally, we collected demographic information, which included general privacy attitudes and whether participants owned any wearable devices.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 comprehension questions (attention checks)
\item 6 questions about various wearables scenarios 
\item 2 questions about smartphone scenarios 
\item 2 risk/benefit questions 
\item 15 demographic questions \\[-.8cm]
\end{itemize}

We randomized the order in which participants completed each section of the survey, as well as the order of the questions within each sections.

\subsection{Question Format} 
In this section, we present the details of each survey section.
